Modeling Intervention Strategies for United States TB Control

### 2014-07-18 in_progress/presentations/paper/draft.tex
added final outline

{\huge \color{red} List of results}
Plan:
\begin{enumerate}
  \item Intervention Analysis: 
    \begin{enumerate}
      \item Reducing Entering LTBI
      \item Cutting Transmission
      \item Reducing Progression Rate
    \end{enumerate}
  \item Qualitative Strategy Conclusions:
    \begin{enumerate}
      \item Sourced Incidence \& Cost
      \item Plateauing Effect
      \item Extremal values for entering LTBI reduction
      \item Linearity in Cost/Incidence for entering LTBI reduction
      \item CPCA data
    \end{enumerate}
  \item Statistical Verification/Agent Based Feasibility
    \begin{enumerate}
      \item Normal Distributions
      \item Basic Reproductive Numbers
      \item Agent based running time \& Extendibility. 
    \end{enumerate}
\end{enumerate}
Ideas:
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}

>>>>

\textbf{Outline for Final Draft}

\begin{description}
  \item[Introduction] Introduce TB, quote WHO about prevelance, note US goals
    for elimination. Recall typical structure of TB disease (Susc. -> LTBI ->
    Active) and note that typical assumptions presumes active is the optimal
    state of the intervention. Note recent work suggesting, in fact, that LTBI
    intervention might also be necessary to acheive elimination goals. Introduce
    possibility of answering that through modeling.

    Recall compartmental models, and introduce Hill model and its findings.
    Introduce our aim. We extended the hill model to provide sourced TB data, so
    as to better analyze what causes US TB incidence. We also added sourced
    economic tracking, so as to analyze US HCS costs due to TB and how various
    intervention strategies affect the US TB load. Finally, we also implement an
    agent based version of The Extended Hill, so as to test its statistical
    accuracy and to establish a new, more extendible framework for modeling
    diseases like TB.

    Our results strongly indicate that the LTBI population and, in particular,
    the immigration to this compartment from infected new arrivals to the US is
    the driving force behind US TB incidence and cost. It also suggests that
    curing incoming LTBI cases upon immigration would be a particularly cost
    effective intervention, and would be necessary if elimination is desired.
    These results are further validated by qualitative effects, such as the
    plateuing effect observed across many interventions, in particular the
    elimination of transmission, and sensitivity analysis.

    The agent based model affirmed the statistical validity of the Hill Model
    and proved to be a computationally realizable framework for disease study in
    general. 
  \item[The Basic Hill]
    Go through the Hill Model in detail. List equations, compartments,
    constants, and meaning. Discuss the fact that this is an approximation of a
    stochastic phenonmena, and thus we cannot be sure it represents
    statistically meaningful data, and discuss pros and cons to agent-based vs
    compartmental models.

    Recall their result about curing LTBI rate. 
  \item[The Extended Hill]
    Explain our strategies for extending the model (splitting equations and
    tracking flows over compartments). Explain adding economic data. Link to
    code github.

    Discuss method of performing sensitivity analysis.

    Explain the agent based hill copy, and the agent based non-hill. Explain
    execution from a theoretical perspective, and in practice (performance,
    language choice, extensibility, etc). 
  \item[Results]
    Document sourced US TB incidence and costs. Demonstrate effects of several
    interventions, among them including eliminating transmission and curing
    entering LTBI and one other. Highlight plateuing effect.

    Discuss outcome of sensitivity analysis on the data, and how it compares to
    results indicated above (e.g. agreement of importance of incoming LTBI cure
    rate and cost).

    Discuss statistical power of results via agent based models. Show
    distributions and give statistics. 
  \item[Discussion]
    Discuss what results indicate about future of TB in US. Indicate that if we
    do not target LTBI population, an endemic future well above elimination is
    all but guaranteed. Discuss the cost effectiveness of curing, for free, all
    incoming cases of LTBI relative to other metrics, such as searching for new
    infected individuals after a case is discovered.

    Discuss the feasibility of using agent based models as a general principle,
    given the ease of use here. Discuss how relevant this will be as
    drug-resistant disease becomes more and more prevalent, as that issue is one
    that compartmental models are ill equipped to track.

    Discuss possibility of extending model to handle drug resistance, HIV
    comorbidity, regional dependence, urban vs rural targeted intervention, etc. 
  \item[Conclusion]
    Final recommendations: Most promising intervention, source of US TB and US
    TB HCS costs, and statistical power of Hill Model (frame it as a nice, but
    unnecessary verification, as this verification wasn't something anyone was
    really asking for). 
\end{description}

\newpage
{\huge \color{red} List of results}
Plan:
\begin{enumerate}
  \item Intervention Analysis: 
    \begin{enumerate}
      \item Reducing Entering LTBI
      \item Cutting Transmission
      \item Reducing Progression Rate
    \end{enumerate}
  \item Qualitative Strategy Conclusions:
    \begin{enumerate}
      \item Sourced Incidence \& Cost
      \item Plateauing Effect
      \item Extremal values for entering LTBI reduction
      \item Linearity in Cost/Incidence for entering LTBI reduction
      \item CPCA data
    \end{enumerate}
  \item Statistical Verification/Agent Based Feasibility
    \begin{enumerate}
      \item Normal Distributions
      \item Basic Reproductive Numbers
      \item Agent based running time \& Extendibility. 
    \end{enumerate}
\end{enumerate}
Ideas:
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}
